Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-06-29 Journal1/paper5TNSM/pr.tex
add sth
add table
add revise

\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously. 
Therefore, we want to study the problem of obtaining the optimal number of VNF, RB assignments, and power allocation to maximize the system's throughput and guarantee the QoS of services. This problem is mixed-integer non-linear programming. Hence, it is difficult to solve and requires some relaxation, convexification, and other methods for obtaining the sub-optimal solution presented in the following sections.}

\subsection{Main Contributions}
The purpose of this paper is twofold. First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC. Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing. Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.

\textcolor{MidnightBlue}{In this paper, we would like to enhance the resource utilization of the overall wireless O-RAN system and optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.}

@@

The rest of this paper is organized as follows.
Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
The system model and the problem formulation are described in Section \ref{systemmodel}. The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Finally, Section \ref{conc} concludes the paper.

\section{Related Literature}\label{RL}
The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered. The network slicing scheme includes a higher level and the lower level. The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), and the allocation of BBU capacity. Also, the allocation of power and physical resource blocks (PRB) is performed at the lower level.
In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).

@@

In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also, the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author discussed the feasible region to make the initial values possible.
\section{Background}\label{BG}
\textcolor{MidnightBlue}{The Open Radio Access Network (O-RAN) is an appropriate alternative to the next generation of radio access networks due to its flexible operations, openness, lower operational costs, and intelligence.}

@@

O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 
\section{System Model and Problem Formulation}\label{systemmodel}
In this section, we describe the downlink system in the O-RAN architecture using RAN slicing as depicted in Figure \ref{fig:c11}.
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the o-ran system. Afterward, we discuss the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
Assume, there are three service types including eMBB, URLLC, and mMTC which support different applications. Accordingly, there are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
Therefore, there are $S$ pre-allocated slices serving these $S$ services ($S = S_1 + S_2 + S_3$);
Hence, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have
$\{1,2,...,S_1\}$ set of eMBB service instances, $\{1,2,...,S_2\}$ set of URLLC service instances, and
$\{1,2,...,S_3\}$ set of mMTC service instances.
Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.

>>>>

\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}

\textcolor{MidnightBlue}{The purpose of this paper is twofold. First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC. Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing. Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.}

\subsection{Main Contributions}

\textcolor{MidnightBlue}{In this paper, we aim to enhance the resource utilization of a downlink O-RAN system and optimize the baseband resource allocation to develop an isolated network slicing outline for different types of services in an O-RAN platform.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.}

@@

The rest of this paper is organized as follows.
Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
The system model and the problem formulation are described in Section \ref{systemmodel}. The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Finally, Section \ref{conc} concludes the paper.
\begin{table}[H]
 \caption {List of Acronyms} \label{table:1a}
 \begin{center}
 \scalebox{0.8}{
  \begin{tabular}{||c | c ||}
  \hline
Abbreviation & Explanation \\ [0.5ex]
  \hline\hline
  VNF & Virtual Network Function\\
  \hline
  VM & Virtual Machine  \\
  \hline
 O-RAN & Open RAN  \\
  \hline
  RAN &  Radio Access Network \\
  \hline
   QoS &  Quality of service \\
  \hline
  PRB &  Physical Resource Block \\
  \hline
  eMBB & enhanced Mobile BroadBand \\
  \hline
  URLLC  & Ultra-Reliable Low Latency Communication \\
   \hline
  mMTC &  massive Machine-To-Machine Communications \\
  \hline
  O-RU &  O-RAN Radio Unit \\
  \hline
   O-DU &  O-RAN Distributed Unit \\ [.5ex]
  \hline
   O-CU &  O-RAN Central Unit \\ [.5ex]
  \hline
  UPF &  User Plane Function \\ [.5ex]
  \hline
 \end{tabular}}
 \end{center}
 \end{table}
\section{Related Literature}\label{RL}
The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered. The network slicing scheme includes a higher level and the lower level. The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), and the allocation of BBU capacity. Also, the allocation of power and physical resource blocks (PRB) is performed at the lower level.
In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).

@@

In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also, the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author discussed the feasible region to make the initial values possible.

\section{Background}\label{BG}
\textcolor{MidnightBlue}{The Open Radio Access Network (O-RAN) is an appropriate alternative to the next generation of radio access networks due to its flexible operations, openness, lower operational costs, and intelligence.}

@@

O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 
%\begin{table}[H]
% \caption {List OF Notation} \label{table:1a}
% \begin{center}
% \scalebox{0.8}{
%  \begin{tabular}{||c | c ||}
%  \hline
%Notation & Description \\ [0.5ex]
%  \hline\hline
%  $S$ & Total number of slices\\
%  \hline
%  $S1$ & Number of eMBB slices  \\
%  \hline
% $S2$ & Number of URLLC slices  \\
%  \hline
%  $S3$ & Number of mMTC slices \\
%  \hline
%   $\bar{K}_s$ & pre-allocated PRB to each slice \\
%  \hline
%  PRB &  Physical Resource Block \\
%  \hline
%  eMBB & enhanced Mobile BroadBand \\
%  \hline
%  URLLC  & Ultra-Reliable Low Latency Communication \\
%   \hline
%  mMTC &  massive Machine-To-Machine Communications \\
%  \hline
%  O-RU &  O-RAN Radio Unit \\
%  \hline
%   O-DU &  O-RAN Distributed Unit \\ [.5ex]
%  \hline
%   O-CU &  O-RAN Central Unit \\ [.5ex]
%  \hline
%  UPF &  User Plane Function \\ [.5ex]
%  \hline
% \end{tabular}}
% \end{center}
% \end{table}
\section{System Model and Problem Formulation}\label{systemmodel}
In this section, we describe the downlink system in the O-RAN architecture using RAN slicing as depicted in Figure \ref{fig:c11}.
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the o-ran system. Afterward, we discuss the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
Assume, there are three service types including eMBB, URLLC, and mMTC which support different applications. Accordingly, there are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
Therefore, there are $S$ pre-allocated slices serving these $S$ services ($S = S_1 + S_2 + S_3$);
Hence, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have
$\{1,2,...,S_1\}$ set of eMBB service instances, $\{1,2,...,S_2\}$ set of URLLC service instances, and
$\{1,2,...,S_3\}$ set of mMTC service instances.
Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
